A holomorphic approach to branes in twisted~$M$-theory

### 2022-09-26 fivebranes/intro.tex
merge error

Let us place this factorization algebra on the threefold $\C^\times \times \C^2$ and consider the reduction along the circle $S^1 \subset \C^\times$. 
In \cite{SWtensor} we have shown that the naive dimensional reduction (where we throw out higher Kaluza--Klein modes along $S^1 \subset \C^\times$) of this factorization algebra agrees with the factorization algebra associated to the minimal twist of perturbative supersymmetric Yang--Mills theory for the group $U(1)$. 
If we keep track of Kaluza--Klein modes, our ansatz is that the full dimensional reduction 
\beqn
\oint_{S^1} \Obs_1
\eeqn
is the factorization algebra associated to the minimal twist of supersymmetric Yang--Mills theory on $\R_{\geq 0} \times \C^2$ including contributions from monopole operators.
In particular, we can recover the Hilbert space of the theory by looking at the value of the factorization algebra along $0 \times \C^2 \subset \R_{\geq 0} \times \C^2$.

>>>>

Let us place this factorization algebra on the threefold $\C^\times \times \C^2$ and consider the reduction along the circle $S^1 \subset \C^\times$. 
In \cite{SWtensor} we have shown that the naive dimensional reduction (where we throw out higher Kaluza--Klein modes along $S^1 \subset \C^\times$) of this factorization algebra agrees with the factorization algebra associated to the minimal twist of perturbative supersymmetric Yang--Mills theory for the group $U(1)$. 
If we keep track of Kaluza--Klein modes, our ansatz is that the full dimensional reduction 
\beqn
\oint_{S^1} \Obs_1
\eeqn
is the factorization algebra associated to the minimal twist of supersymmetric Yang--Mills theory on $\R_{\geq 0} \times \C^2$ including contributions from instanton operators.\footnotes{The instanton charge turns out to be identical to the winding number around $S^1$.}
In particular, we can recover the Hilbert space of the theory by looking at the value of the factorization algebra along $0 \times \C^2 \subset \R_{\geq 0} \times \C^2$.
